Power simulation section

### 2023-08-04 docs/manuscript.Rmd
increase the simulation design

```{r, message=FALSE, eval=FALSE}
library(future)
plan("multisession", workers = 4)
set.seed(2)
```

@@

```{r, eval=FALSE}
library(furrr)
sim_design <- crossing(
  rep = 1:250,
  n_subjects = c(100, 150, 200),
  n_items = c(10, 30, 50)
) %>%
  mutate(pvalues = future_pmap(., sim_and_analyse, 
    .options = furrr_options(seed = TRUE))) %>%
  unnest_wider(pvalues)
```

@@

```{r, eval=FALSE}
library(binom)
alpha <- 0.05
power <- sim_design %>%
  group_by(n_subjects, n_items) %>% 
  summarise(power = mean(p_H01 < alpha & p_H02 < alpha & 
                           p_H03 < alpha & p_H04 < alpha), 
    n_sig = sum(p_H01 < alpha & p_H02 < alpha & 
                  p_H03 < alpha & p_H04 < alpha),
    n = n(),
    ci.lwr = binom.confint(n_sig, n, method = "wilson")$lower,
    ci.upr = binom.confint(n_sig, n, method = "wilson")$upper, 
    .groups = "drop")
power %>%
  mutate(across(c(n_subjects, n_items), factor)) %>%
  ggplot(aes(n_subjects, n_items, fill = power)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f \n [%.2f; %.2f]", 
                                power, ci.lwr, ci.upr)), 
    color = "white", size = 6) +
  scale_fill_viridis_c(limits = c(0, 1))
```

>>>>

```{r, message=FALSE, eval=TRUE}
library(future)
plan("multisession", workers = 6)
set.seed(2)
```

@@

```{r, message=FALSE, eval=TRUE}
library(furrr)
sim_design <- crossing(
  rep = 1:300,
  n_subjects = c(100, 150, 200, 250),
  n_items = c(10, 30, 50, 70)
) %>%
  mutate(pvalues = future_pmap(., sim_and_analyse, 
    .options = furrr_options(seed = TRUE))) %>%
  unnest_wider(pvalues)
```

@@

```{r, eval=TRUE}
library(binom)
alpha <- 0.05
power <- sim_design %>%
  group_by(n_subjects, n_items) %>% 
  summarise(power = mean(p_H01 < alpha & p_H02 < alpha & 
                           p_H03 < alpha & p_H04 < alpha), 
    n_sig = sum(p_H01 < alpha & p_H02 < alpha & 
                  p_H03 < alpha & p_H04 < alpha),
    n = n(),
    ci.lwr = binom.confint(n_sig, n, method = "wilson")$lower,
    ci.upr = binom.confint(n_sig, n, method = "wilson")$upper, 
    .groups = "drop")
power %>%
  mutate(across(c(n_subjects, n_items), factor)) %>%
  ggplot(aes(n_subjects, n_items, fill = power)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f \n [%.2f; %.2f]", 
                                power, ci.lwr, ci.upr)), 
    color = "white", size = 6) +
  scale_fill_viridis_c(limits = c(0, 1))
```
